\documentclass{tccv-master/tccv}
\usepackage[english]{babel}
\usepackage{nth}

\begin{document}

\part{Emmanuel Breton-Belz}

\section{Work experience}

\begin{eventlist}

\item{July 2017 -- Present}
     {Artal Technologies, Toulouse}
     {Full stack Eclipse RCP Development}

Software development for Airbus model simulation process: Creation of 
front-end components using Nebula Nattables and Sirius Plugin for instance.
Participation in the migration from \href{https://www.eclipse.org/cdo/}{CDO} to Hibernate
persistence framework. Creation and optimization of JPA queries to retrieve 
data in back-end. Strong knowledge in modular development.

\item{November 2016 -- April 2017}
     {Bosch, Abstatt}
     {Full stack Eclipse RCP Development}

Software development for automotive controller management and design:
Front-end using JFace wizards to retrieve users need and persistence using 
SAX/DOM. Advanced version system of XSD schema using Eclipse built in
features.

\item{May -- July 2015}
     {DIEM, Salerno}
     {Object detection}
Creation of object recognition using SURF feature detector with OpenCV.
Programming in C++, and dealing with image loading, processing, feature extraction
and feature enhancement for research purposes.

\end{eventlist}

\section{Scholar experience}

\begin{eventlist}
\item{June 2016}
{UNISA, Salerno}
     {Vision cup}
Competition for artificial vision course. Teams of three building software guiding 
Nao robot through a visually marked path and \href{https://github.com/manumanmax/Nao}{classify objects} along the path.

\item{2015}
{ENSICAEN, Caen - UNISA, Salerno}
     {Image analysis} \\
Theory and practice of image analysis, 3D representation, shape and objects segmentation and classification.
Labs using video games development support and image analysis. 

\end{eventlist}
\personal
    [www.funforfox.com]
    {10 all\'ee des violettes\newline 31520 -- Ramonville-Saint-Agne\newline \nth{5} of October 1993}
    {+33 (0) 679122243}
    {emmanuelbretonbelz@gmail.com}

\section{Education}

\begin{yearlist}

\item[Computer sciences]{2015 -- 2017}
     {Master's degree}
     {UNISA Ingeneria, Salerno}

\item[Informatics, image]{2013 -- 2017}
     {Engineer diploma}
     {ENSICAEN, Caen}

\item[Informatics, image]{2011 -- 2013}
     {Technical degree}
     {IUT, Caen}

\end{yearlist}

\section{Communication skills}

\begin{factlist}
\item{French}{Native speaker}
\item{English}{820 points TOIEC, fluent}
\item{Italian}{Fluent}
\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Professional}
	{Java 8, Eclipse RCP3}
\item{Good level}
     {C++/C, SQL, Oracle, git, subversion, Jira, JUnit}

\item{Intermediate}
     {Python, \LaTeX, PHP, JS, HTML, CSS, OpenCV, DL4J, J2EE, C\#, Matlab, Jenkins}

\item{Basic level}
     {NodeJS, React.js, Unity}

\end{factlist}

\section{Hobbies}

\begin{factlist}

\item{Reading}
	{Deep learning: A practitioner approach}
\item{Interests}
	{Nutrition, neuro-science, body kinetic, permaculture}
\item{Sports}
	{Triathlon, trail, handball}
\end{factlist}
\newpage




\section{Software details}

\begin{eventlist}

\item
{Java}
{A year and a half}
{Professional experience}\\
Using Java 8 at work for one year and a half.
Knowledge in Maven project compilation, threads synchronization and analysis with JVisualVM, advanced OOP and data-binding.
Modular programming using OSGi platform for complex systems development with Eclipse RCP.
3 month project of spaceship game for Scrum team development labs.
Following Java user group meetups about Java and Kotlin. 

\item
{C/C++}
{3 month}
{Scholar and internship experience}\\
Embedded development of automated barrier opening using proximity sensors and NFC with STM32F3 at UNISA.
Embedded development using Raspberry pi at UNISA, PIC18 with 8bit processor constraints at ENSICAEN.
2 month C++ development during DIEM lab internship 
Advanced courses at Ensicaen with C++ 11 with preference for clang compiler.
Labs using QtCreator for Qt development at Ensicaen.
Advanced linux process, threads, semaphores and memory management.
Competition lab for shortest path algorithm programming on simulated car circuit at ENSICAEN.


\item
{Persistence}
{A year and a half}
{Professional experience}\\
Use of Sax/Dom in Java during internship at Bosch with XSD versioning.
Use of Hibernate with emf/jpa binding for metamodel persistence. 
Debug and optimisation of SQLQueries on H2 with high dependency constraints on metamorphism.
Intense use of Oracle during technical degree with Oracle SGBD on Tour de France database server.
Use of MySQL for php labs, postgreSQL for project labs at ENSICAEN, SQLite for Technical degree final project.

\item{Web development}
{Labs}
{Scholar experience}\\
Php/HTML/CSS labs in technical degree.
J2EE labs and e-commerce like website development to use servlet mapping, cookies and logging.
Ajax lists development during labs.
Simple personal website using npm react.js's bootstrap.
SSL certification using Certbot on raspbian.

\item{Script languages}
{Labs}
{Scholar experience}\\
Python: \\
Blender script development for random tree trunk and branches modeling. 
AI lab serious game development solving Packman levels.
OpenCV labs in Salerno using python for image analysis.\\\\
Matlab:\\
Robotic labs using matlab and simulink for kinetic computation with VRep for 3D representation.
Data mining labs at ENSICAEN for dataset principal component analysis and neural networks development and training.
Source and channel codification and compression labs at UNISA developing different algorithms with Soft and Hard coding.\\\\
JavaScript:\\
Compilation and test of OpenCV.js with emscripten for Web integration of OpenCV.
Labs using JS scripts and functions inside HTML.
Hosted at home Node.js personal website.

\item
{Image analysis and synthesis}
{Labs}
{Scholar experience}\\
Plane images enhancement at UNISA Lab using high resolution with low spectral range and low resolution with high spectral range images fusion.
Image analysis using OpenCV and Greyc Pandore toolkit at ENSICAEN.
OpenCL game development at ENSICAEN Lab.\\
Unity CSharp serious game development to promote Virtual reality at ENSICAEN using Oculus rift. 2 month development of objects on image detection using SWIFT feature extraction.
Personal project of face recognition using OpenCV with java.

\item
{Data science}
{Project and Labs}
{Scholar and personal experience}\\
Homemade cascade classifier using K-means algorithm to detect objects from Nao camera images.
Neural network development for machine learning lab at ENSICAEN during data mining courses.
Training using various handmade simple feature extraction and data sets:\\
\href{https://github.com/manumanmax/Nao}{github.com/manumanmax/Nao}.\\
Following Toulouse Data Science (TDS) meetups about Blockchains and Keras Tensorflow module.


\end{eventlist}

\end{document}
