\documentclass{tccv-master/tccv}
\usepackage[english]{babel}

\begin{document}

\part{Emmanuel Breton-Belz}

\personal
    {2 impasse des Roquerets, 14500 Vire Normandie, France}
    {+33 (0) 679122243}
    {emmanuelbretonbelz@gmail.com}
\section{Work experience}

\begin{eventlist}

\item{Novembre 2021}
     {Radicelle, anywhere}
     {Full stack multi-platform Flutter}\\
 I realized the app I was building had more potential if it was to be in Flutter so I learned and reworked it with Flutter. Now I am learning Go and Rust in order to replace Ktor with Gin or Rocket.
 
\item{December 2020}
     {Radicelle, anywhere}
     {Full stack Web dev+Ops ReactJS/Ktor}
I founded Radicelle which owns \mbox{radicelle.eu}. It will be series of web platforms willing to ease "neo rural" people in
selling agricultural products, develop their production systems and boost their local distribution by proposing simple 
and affordable services. Its stack is:\\
$\bullet$ Frontend : ReactJS eased by Material-UI\\
$\bullet$ KMongo connected to Mongo Atlas.\\
$\bullet$ Backend : Ktor to expose REST APIs interfacing back and front entities using Kotlinx Serialization.\\
$\bullet$ Kotlin gradle DSL for building the project. Featuring plugin DSLs and pre build features.

\item{October 2018 -- December 2020}
     {Eurecia, Toulouse}
     {Full stack Web developer}
Carrying out three main tasks, first maintaining java over struts + jsp legacy eurecia.com platform code.
The second was developing new features using REST API with Java and lately Kotlin (including spec challenging).
The third was developing VueJS components calling the REST APIs we created and bind them to the legacy JSP struts architecture.
Using Spring annotations and sometimes plain SQL to communicate whit a MariaDB database, my team and I were responsible for 
implementation, integration and optimization estimations and establishment in order for the code to be production grade.


\item{July 2017 -- September 2018}
     {Artal Technologies, Toulouse}
     {Full stack Eclipse RCP Development}

Software development for Airbus model simulation process: Creation of 
front-end components using Nebula Nattables and Sirius Plugin for instance.
Participation in the migration from \href{https://www.eclipse.org/cdo/}{CDO} to Hibernate
persistence framework. Creation and optimization of JPA queries to retrieve 
data in back-end. Strong knowledge in modular development.

\item{November 2016 -- April 2017}
     {Bosch, Abstatt}
     {Full stack Eclipse RCP Development}

Software development for automotive controller management and design:
Front-end using JFace wizards to retrieve users need and persistence using 
SAX/DOM. Advanced version system of XSD schema thanks Eclipse built in
features.


\end{eventlist}

\section{Education}

\begin{yearlist}

\item[Computer sciences]{2015 -- 2017}
     {Master's degree}
     {UNISA Ingeneria, Salerno}

\item[Informatics, image]{2013 -- 2017}
     {Engineer diploma}
     {ENSICAEN, Caen}

\item[Informatics, image]{2011 -- 2013}
     {Technical degree}
     {IUT, Caen}

\end{yearlist}

\section{Scholar challenge}

\begin{eventlist}
\item{June 2016}
{UNISA, Salerno}
     {Vision cup}
Competition for artificial vision course. Teams of three building software guiding 
Nao robot through a visually marked path and classify objects along the path (github link \href{https://github.com/manumanmax/Nao}{here}).


\end{eventlist}
\pagebreak

\section{Communication skills}

\begin{factlist}
\item{French}{Mother tongue}
\item{English}{820 points TOIEC, fluent}
\item{Italian}{Fluent}
\item{German}{B1}
\end{factlist}


\section{Software skills}

\begin{factlist}

\item{Professional level}
	{Intellij, Kotlin, Java 8, git, MongoDB, MariaDB, Spring, SQL, REST}
\item{Good level}
     {Dart, Flutter, object design patterns, C++/C, Oracle, subversion, Jira, JUnit, \LaTeX, VueJS, HTML/CSS}
\item{Intermediate}
     {Functionnal programing, React.js, Python, PHP, JS, OpenCV, DL4J, J2EE, C\#, Matlab, Jenkins}

\item{Basic level}
     {Golang, TensorFlow, NodeJS, Unity}

\end{factlist}

\section{Hobbies}

\begin{factlist}

\item{Readings}
	{Medium digest (Kotlin section), Deep learning: A practitioner approach}
\item{Interests}
	{Sciences (health, economy, astrophysics, biomechanics,...), agriculture, Japanese culture, video games}
\item{Sports}
	{Trail (running), cycling, monofin swimming}
\end{factlist}

\end{document}
